---
title: "Balance and District tables"
author: "Ananya Mazumder"
date: "2026-02-10"
output: word_document
---


```{r "setting up the data", include=FALSE, echo=FALSE}
library(haven)
library(tidyverse)
library(survey)
library(gtsummary)
library(xfun)
library(broom)
library(here)
library(labelled)
library(tableone)
library(flextable)

data_2019 <- read_stata(here("data", "2019_final.dta"))

data_2019 <- data_2019 %>%
  mutate(
    v131 = to_factor(v131),
    v131 = case_when(
      v131 %in% c("caste", "tribe", "no caste / tribe", "don't know") ~ v131,
      TRUE ~ factor(NA, levels = levels(v131))    
      ) %>%
      set_variable_labels(v131 = "ethnicity")
  )

data_2019 <- data_2019 %>%
  mutate(
    v437 = case_when(
      v437 < 9000 ~ v437 / 10,
      TRUE ~ NA_real_
    ),
    v438 = case_when(
      v438 < 9000 ~ v438 / 10,
      TRUE ~ NA_real_
    )
  ) %>%
  set_variable_labels(
    v437 = "Weight (kg)",
    v438 = "Height (cm)"
  )

var_labels <- data_2019 %>% 
  map(~attr(., "label")) %>% 
  compact()

data_2019 <- data_2019 %>%
  mutate(across(everything(), ~{
    if (is.labelled(.)) {
      lbls <- val_labels(.)
      return(if_else(. >= 95 & . %in% lbls, NA_real_, as.numeric(.)))
    }
    return(.)
  })) %>%
  unlabelled() %>%
  mutate(across(where(is.numeric), ~zap_labels(.)))

data_2019 <- data_2019 %>% 
  mutate(treated_district = ifelse(
    shdist %in% c(214, 367, 273, 220, 169, 930, 871, 122, 130, 291, 
                  825, 302, 287, 328, 339, 248, 60, 357, 242, 842, 
                  412, 69, 470, 36, 321, 847, 488, 900, 562, 49, 
                  581, 546, 28, 593, 585), 1, 0
  ))

data_2019 <- data_2019 %>% 
  mutate(eligibility_status = case_when(
    v012 >= 21  & 
      ((b2_01 >= 2012 & b2_01 <= 2016) | 
         (b2_02 >= 2012 & b2_02 <= 2016 & !is.na(b2_02))) ~ 1,
    
    v012 >= 21  &
      ((b2_01 >= 2005 & b2_01 < 2009) | 
         (b2_02 >= 2005 & b2_02 < 2009 & !is.na(b2_02))) ~ 0,
  ))


data_2019 <- data_2019 %>% 
  set_variable_labels(.labels = var_labels, .strict = FALSE)

data_2019$wt_women <- data_2019$v005/1000000
data_2019$wt_men <- data_2019$mv005/1000000
data_2019 <- data_2019 %>%
  mutate(
    combined_group = interaction(
      haven::as_factor(eligibility_status), 
      haven::as_factor(treated_district), 
      sep = " × "
    )
  )
data_2019$v012_sq <- data_2019$v012^2
attr(data_2019$v012_sq, "label") <- "Square of Women's Age"

controls_hh <- c("v131","v136","v137","v151","v152","v119","v120", "v121", "v122", "v123", "v124", "v125", "mv190", "sm190s")
controls_women <- c("v012", "v012_sq", "v133","v437", "v438", "v511", "d113", "v201", "v715", "v714")
controls_men <- c("mv035", "mv133", "mv212", "mv190a", "sm190s", "mv714") ##added also the wealth indices and a variable for currently working or not 

data_2019 <- data_2019 %>%
  mutate(
    v739_any_say = ifelse(!is.na(v739), ifelse(v739 %in% c(1, 2), 1, 0), NA),
    v743a_any_say = ifelse(!is.na(v743a), ifelse(v743a %in% c(1, 2), 1, 0), NA),
    v743b_any_say = ifelse(!is.na(v743b), ifelse(v743b %in% c(1, 2), 1, 0), NA),
    v743d_any_say = ifelse(!is.na(v743d), ifelse(v743d %in% c(1, 2), 1, 0), NA),
    v743f_any_say = ifelse(!is.na(v743f), ifelse(v743f %in% c(1, 2), 1, 0), NA)
  )
##any_say variables are constructed such that women responding to decision-making questions with 1 or 2 become 1 (yes, autonomy) and if not, then 0 (not autonomous)
# Then the autonomy index is created using those binary variables
data_2019 <- data_2019 %>%
  mutate(
    # Count non-missing responses
    n_answered = rowSums(!is.na(across(c(v739_any_say, v743a_any_say, 
                                         v743b_any_say, v743d_any_say, 
                                         v743f_any_say)))),
    
    # Autonomy index: only if all 5 answered
    autonomy_index = ifelse(n_answered == 5,
                            rowMeans(across(c(v739_any_say, v743a_any_say, 
                                              v743b_any_say, v743d_any_say, 
                                              v743f_any_say)), na.rm = TRUE),
                            NA),
    
    # Autonomy dummy: only if all 5 answered
    autonomy_dummy = ifelse(n_answered == 5,
                            ifelse(rowSums(across(c(v739_any_say, v743a_any_say,
                                                    v743b_any_say, v743d_any_say, 
                                                    v743f_any_say)), na.rm = TRUE) > 0, 1, 0),
                            NA)
  )

group_counts <- data_2019 %>%
  filter(!is.na(combined_group)) %>%
  count(combined_group) %>%
  arrange(combined_group)

data_men <- data_2019 %>% filter(!is.na(mv021))

mysurvey_men <- svydesign(
  id = ~mv021, 
  strata = ~mv022,
  weights = ~wt_men,
  data = data_men,
  nest = TRUE
)

mysurvey_women <- svydesign(
  id = ~v021,
  strata = ~v022, 
  weights = ~wt_women,
  data = data_2019,
  nest = TRUE
)

options(survey.lonely.psu = "adjust") 

outcomes_dec <- c("v739", "v743a", "v743b", "v743d", "v743f") 
outcomes_ipv <- c("d106", "d107", "d108", "d129")
outcomes_work <- c("v714", "v714a", "v746", "v731")

```
Table for IGMSY districts 

```{r "IGMSY districts", echo=FALSE}
districts_data <- tibble(
  development_level = c(
    rep("Low", 10),
    rep("Middle", 19),
    rep("High", 7)
  ),
  pilot_district = c(
    # Low
    "Saharsa", "Simdega", "Tamenglong", "Vaishali", "Mahoba", 
    "Sultanpur", "East Garo Hills", "Bhilwara", "Udaipur", "Dhalai",
    # Middle
    "Bastar", "Goalpara", "Lawngtlai", "Jalpaiguri", "Bankura",
    "Papumpare", "Dehradun", "Purbi Singhbhum", "West District", 
    "North West Delhi", "Dhamtari", "Panchkula", "Patan", "Kapurthala",
    "Kamrup", "West Delhi", "Bharuch", "Nalgonda", "YSR",
    # High
    "Dharwad", "Amritsar", "Kolar", "West Godavari", "Hamirpur", 
    "Palakkad", "North Goa"
  ),
  pilot_state = c(
    # Low
    "Bihar", "Jharkhand", "Manipur", "Bihar", "UP",
    "UP", "Meghalaya", "Rajasthan", "Rajasthan", "Tripura",
    # Middle
    "Chhattisgarh", "Assam", "Mizoram", "West Bengal", "West Bengal",
    "Arunachal Pradesh", "Uttarakhand", "Jharkhand", "Sikkim",
    "Delhi", "Chhattisgarh", "Haryana", "Gujarat", "Punjab",
    "Assam", "Delhi", "Gujarat", "Telengana", "Andhra Pradesh",
    # High
    "Karnataka", "Punjab", "Karnataka", "Andhra Pradesh", "Himachal Pradesh", 
    "Kerala", "Goa"
  ),
  control_district = c(
    # Low
    "Katihar", "Godda", "Muzaffarnagar", "Saran", "Azamgarh",
    "West Garo Hills", "Banswara", "Ukhrul", "Bilaspur", "",
    # Middle
    "Tonk", "Dhemaji", "Ranchi", "North Tripura", "Changlang",
    "Chamoli", "Puruliya", "Durg", "Mamit", "Dakshin Dinajpur",
    "South Delhi", "South District", "Rewari", "Fatehgarh Sahib",
    "Valsad", "Dibrugarh", "Kheda", "East Delhi", "",
    # High
    "Davangere", "Bilaspur", "Muktsar", "Rangareddy", "Tumkur", 
    "Kozhikode", "South Goa"
  ),
  control_state = c(
    # Low
    "Bihar", "Jharkhand", "Uttar Pradesh", "Bihar", "Uttar Pradesh",
    "Meghalaya", "Rajasthan", "Manipur", "Chhattisgarh", "",
    # Middle
    "Rajasthan", "Assam", "Jharkhand", "Tripura", "Arunachal Pradesh",
    "Uttarakhand", "West Bengal", "Chhattisgarh", "Mizoram", "West Bengal",
    "Delhi", "Sikkim", "Haryana", "Punjab", "Gujarat",
    "Assam", "Gujarat", "Delhi", "",
    # High
    "Karnataka", "Himachal Pradesh", "Punjab", "Telengana", "Karnataka", 
    "Kerala", "Goa"
  )
)

options(survey.lonely.psu = "adjust")

districts_table <- districts_data %>%
  flextable() %>%
  set_caption("Table 1: District Selection for IGMSY Pilot Program by Development Level") %>%
  set_header_labels(
    development_level = "Development Level",
    pilot_district = "District",
    pilot_state = "State",
    control_district = "District",
    control_state = "State"
  ) %>%
  add_header_row(
    values = c("", "Pilot", "Control"),
    colwidths = c(1, 2, 2)
  ) %>%
  theme_booktabs() %>%
  autofit() %>%
  align(align = "left", part = "all")

districts_table

```

Next comes the balance table: 

```{r "Balance Table", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}

data_2019 <- data_2019 %>%
  mutate(
    balance_group = case_when(
      treated_district == 0 & eligibility_status == 0 ~ "Control × Non-eligible",
      treated_district == 0 & eligibility_status == 1 ~ "Control × Eligible",
      treated_district == 1 & eligibility_status == 0 ~ "Treatment × Non-eligible",
      treated_district == 1 & eligibility_status == 1 ~ "Treatment × Eligible"
    )
  )

balance_survey <- svydesign(
  id = ~v021,
  strata = ~v022, 
  weights = ~wt_women,
  data = data_2019,
  nest = TRUE
)

tab_control <- balance_survey %>%
  subset(treated_district == 0) %>%
  tbl_svysummary(
    by = balance_group, # This should now only have 2 levels (Eligible/Non-eligible)
    include = c(all_of(outcomes_dec), all_of(outcomes_work), 
                all_of(outcomes_ipv), all_of(controls_hh), 
                all_of(controls_women)),
    statistic = list(all_continuous() ~ "{mean}",
                     all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  ) %>%
  add_p(test = list(all_continuous() ~ "svy.t.test", 
                    all_categorical() ~ "svy.chisq.test"))

# 2. Create Table for Treated Districts (treated_district == 1)
tab_treated <- balance_survey %>%
  subset(treated_district == 1) %>%
  tbl_svysummary(
    by = balance_group,
    include = c(all_of(outcomes_dec), all_of(outcomes_work), 
                all_of(outcomes_ipv), all_of(controls_hh), 
                all_of(controls_women)),
    statistic = list(all_continuous() ~ "{mean}",
                     all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  ) %>%
  add_p(test = list(all_continuous() ~ "svy.t.test", 
                    all_categorical() ~ "svy.chisq.test"))

# 3. Merge them into one master balance table
balance_table <- tbl_merge(
  tbls = list(tab_control, tab_treated),
  tab_spanner = c("**Control Districts**", "**Treatment Districts**")
) %>%
  modify_caption("**Table S1.1. Balance between Eligible and Non-eligible Cohorts**")