---
title: "Brief_outline_data"
author: "Ananya Mazumder"
date: "2025-12-16"
output: word_document
---
Descriptives: included here are tables for women, household and for men. The variables included are the controls included later on in the regressions. 
```{r "setting up the data", include=FALSE, echo=FALSE}
library(haven)
library(tidyverse)
library(survey)
library(gtsummary)
library(xfun)
library(stargazer)
library(here)

data_2019 <- read_stata(here("data", "2019_final.dta"))

data_2019 <- data_2019 %>% 
  mutate(treated_district = ifelse(
    shdist %in% c(214, 367, 273, 220, 169, 930, 871, 122, 130, 291, 
                  825, 302, 287, 328, 339, 248, 60, 357, 242, 842, 
                  412, 69, 470, 36, 321, 847, 488, 900, 562, 49, 
                  581, 546, 28, 593, 585), 1, 0
  ))

data_2019 <- data_2019 %>% 
  mutate(eligibility_status = case_when(
    v012 >= 21  & 
      ((b2_01 >= 2012 & b2_01 <= 2016) | 
         (b2_02 >= 2012 & b2_02 <= 2016 & !is.na(b2_02))) ~ 1,
    
    v012 >= 21  &
      ((b2_01 >= 2005 & b2_01 < 2009) | 
         (b2_02 >= 2005 & b2_02 < 2009 & !is.na(b2_02))) ~ 0,
      ))


data_2019$wt_women <- data_2019$v005/1000000

data_2019$wt_men <- data_2019$mv005/1000000

data_2019 <- data_2019 %>%
  mutate(
    combined_group = interaction(
      haven::as_factor(eligibility_status), 
      haven::as_factor(treated_district), 
      sep = " × "
    )
  )

data_men <- data_2019 %>% filter(!is.na(mv021))

mysurvey_men <- svydesign(
  id = ~mv021, 
  strata = ~mv022,
  weights = ~wt_men,
  data = data_men,
  nest = TRUE
)

mysurvey_women <- svydesign(
  id = ~v021,
  strata = ~v022, 
  weights = ~wt_women,
  data = data_2019,
  nest = TRUE
)

options(survey.lonely.psu = "adjust")  

controls_hh <- c("v119","v120", "v121", "v122", "v123", "v124", "v125", "v131", "v136", "v137", "v151", "v152", "mv190", "sm190s")
controls_women <- c("v012", "v133","v437", "v438", "v511", "d113", "v201", "v715", "v714")
controls_men <- c("mv035", "mv133", "mv212")
```

```{r "First descriptive table", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}

desc_table_1 <- mysurvey_women %>%
  tbl_svysummary(
    include = all_of(controls_women),
    by = combined_group,
    statistic = list(
      all_continuous() ~ "{mean}\n({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 3,
    missing = "no"
  ) %>%
  modify_caption("**Table 1. Survey-Weighted Descriptives for Women**") %>%
  modify_header(
    stat_1 ~ "**Control District × Ineligible**  \nN= {n}",
    stat_2 ~ "**Treated District × Ineligible**  \nN= {n}", 
    stat_3 ~ "**Control District × Eligible**  \nN= {n}",
    stat_4 ~ "**Treated District × Eligible**   \nN= {n}"
  ) %>%
  modify_footnote(all_stat_cols() ~ "Mean (SD) for continuous variables; N (%) for categorical variables. 0 = no, 1 = yes for binary variables.")
desc_table_1 %>% as_gt()
```



```{r "second descriptive-table", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
desc_table_2 <- mysurvey_men %>%
  tbl_svysummary(
    include = all_of(controls_men),
    by = combined_group,
    statistic =list(
      all_continuous() ~ "{mean}\n({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 3,
    missing = "no"
  ) %>%
  add_n() %>% 
  modify_caption("**Table 2. Survey-Weighted Descriptives for Men**") %>%
  modify_header(
  stat_1 ~ "**Control District × Ineligible**  \nN = {n}",
  stat_2 ~ "**Treated District × Ineligible**  \nN = {n}", 
  stat_3 ~ "**Control District × Eligible**  \nN = {n}",
  stat_4 ~ "**Treated District × Eligible**  \nN = {n}"
) %>%
  modify_footnote(all_stat_cols() ~ "Mean (SD) for continuous variables; N (%) for categorical variables. 0 = no, 1 = yes for binary variables.")
desc_table_2 %>% as_gt() 
```

The table above displays certain characteristics of men in the sample. These men are married, and matched to women in the sample. 

````{r "third descriptive-table", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
desc_table_3 <- mysurvey_women %>%
  tbl_svysummary(
    include = all_of(controls_hh), 
    by = combined_group,
    statistic = list(
      all_continuous() ~ "{mean}\n({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 3,
    missing = "no",
    label = list(
      mv190 ~ "Wealth Index (National)",
      sm190s ~ "Wealth Index (Within State)"  
    )
  ) %>%
  modify_caption("**Table 3. Survey-Weighted Household Characteristics**") %>%
  modify_header(
    stat_1 ~ "**Control District × Ineligible**  \nN = {n}",
    stat_2 ~ "**Treated District × Ineligible**  \nN = {n}", 
    stat_3 ~ "**Control District × Eligible**  \nN = {n}",
    stat_4 ~ "**Treated District × Eligible**  \nN = {n}"
  ) %>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD) for continuous variables; N (%) for categorical variables. Wealth indices: 1 = Poorest, 5 = Richest. Sex of HH head: 1 = Male, 2 = Female. Ethnicity: 991 = Caste, 992 = Tribe, 993 = No caste/tribe, 998 = Don't know. Binary variables: 0 = No, 1 = Yes, 7 = Not a dejure resident (where applicable)."
  )

desc_table_3 %>% as_gt()

````

Regressions

````{r "women's decision-making models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_dec <- c("v739", "v743a", "v743b", "v743d", "v743f") 

# Run models
model_results_1 <- list()
for (i in outcomes_dec) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status * treated_district"))  # Simplified formula
  
  model_i <- tryCatch({
    svyglm(formula_i, design = mysurvey_women)  # Removed redundant data argument
  }, 
  error = function(e) {
    message(paste("Error fitting model for", i, ":", e$message)) 
    return(NULL)
  }) 
  
  if (!is.null(model_i)) {
    model_results_1[[i]] <- model_i
  }
}

# Define custom labels
custom_labels <- c(
  "Own Earnings",
  "Own Healthcare", 
  "Large Purchases",
  "Visiting Family",      
  "Husband's Money"  
)

# Create regression tables and merge
tbl_list <- lapply(model_results_1, function(model) {  # Simplified - iterate directly over models
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_labels
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


## DiD, with controls ##

# Run models
model_results_2 <- list()
for (i in outcomes_dec) {
  
  controls_all <- c(controls_women, controls_hh)
  controls_formula <- paste(controls_women, collapse = " + ")
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula))   
  model_i <- tryCatch({
    svyglm(formula_i, design = mysurvey_women)  
  }, 
  error = function(e) {
    message(paste("Error fitting model for", i, ":", e$message)) 
    return(NULL)
  }) 
  
  if (!is.null(model_i)) {
    model_results_2[[i]] <- model_i
  }
}


# Create regression tables and merge
tbl_list <- lapply(model_results_2, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_labels
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


````

These are my main results. 

```{r, "IPV Models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_ipv <- c("d106", "d107", "d108", "d129")
model_results_3 <- list()
for (i in outcomes_ipv) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  model_i <- tryCatch({
    svyglm(formula_i, design= mysurvey_women)
  }, 
  error= function(e){
    message(paste("Error fitting model for", i, ":", e$message)) 
    return(NULL)
  })
  
  if (!is.null(model_i)) {
    model_results_3[[i]] <- model_i
  }
}
custom_2 <- c("Less Severe Violence", "Severe Violence", "Sexual Violence", "Afraid of Husband")

tbl_list <- lapply(model_results_3, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_2
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


##Regressions with controls ##
outcomes_ipv <- c("d106", "d107", "d108", "d129")
model_results_4 <- list()
for (i in outcomes_ipv) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula)) 
  model_i <- tryCatch({
    svyglm(formula_i, design= mysurvey_women)
    }, 
  error= function(e){
    message(paste("Something got messed up somehow", i, ":", e$message)) 
    return(NULL)
  })
  
  if (!is.null(model_i)) {
    model_results_4[[i]] <- model_i
  }
}

tbl_list <- lapply(model_results_4, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_2
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()
```

Men's Attitudes towards violence, and IPV, decision-making
```{r, "Men's Models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_men_1 <-c("mv633a", "mv633b", "mv633d", "mv634a", "mv634b", "mv634c", "mv634d") ##wife can refuse sex
outcomes_men_2 <-c("mv739", "mv743a", "mv743b") #person who decides on certain things
outcomes_men_3 <-c("mv744a", "mv744b", "mv744c", "mv744d", "mv744e") #violence justified 
custom_men_1 <-c("Refuse in case husband has sti", "Refuse in case husband has other women", "Refuse in case wife is tired", 
                 "Refuse: right to get angry", "Refuse: right to withhold financial means", "Refuse: right to use force", 
                 "Refuse, right to have sex with another woman")
custom_men_1 <-c("Refuse sex in case husband has sti", "Refuse sex in case husband has other women", "Refuse sex in case wife is tired", 
                 "Refuse sex: right to get angry", "Refuse sex: right to withhold financial means", "Refuse sex: right to use force", 
                 "Refuse sex, right to have sex with another woman")
custom_men_2 <-c("Own Earnings", "Healthcare", "Large Purchases")
custom_men_3 <-c("Justified: wife goes out without telling", "Justified: wife neglects the children", "Justified: wife argues with husband", "Justified: wife refuses to have sex", "Justified: wife burns food")

##Refusing sex Models without controls##
model_results_5 <- list()

for (i in outcomes_men_1) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_5[[i]] <- model_i
  }
} 
tbl_list <- lapply(model_results_5, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_1
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


##Decision making models without controls ##
model_results_6 <- list()

for (i in outcomes_men_2) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_6[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_6, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_2
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

## Violence models, without controls
model_results_7 <- list()

for (i in outcomes_men_3) {
  
  controls_formula <- paste(controls_women, collapse = " + ")
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_7[[i]] <- model_i
  }
} 


## summarizing output 
tbl_list <- lapply(model_results_7, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_3
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


##Men Models with controls##

model_results_8 <- list()

for (i in outcomes_men_1) {
  controls_all_men <- c(controls_men, controls_hh)
  controls_formula <- paste0(controls_all_men, collapse = " + ")
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula))
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men)
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_8[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_8, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_1
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

##Decision making models with controls ##
model_results_9 <- list()

for (i in outcomes_men_2) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula)) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_9[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_9, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_2
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

## Violence models, without controls
model_results_10 <- list()

for (i in outcomes_men_3) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula)) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_10[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_10, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_3
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

```

Economic Participation of Women

```{r, "Women's Economic Participation Models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_work <- c("v714", "v714a", "v746", "v731")
model_results_11 <- list()
custom_3 <- c("currently working", "has a job, currently absent", "earns more than husband", "worked in last 12 months")

for (i in outcomes_work) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status"))
  model_i <- tryCatch({
    
    svyglm(formula_i, 
           design = mysurvey_women,
    ) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_11[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_11, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_3
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

##with controls 
model_results_12 <- list()
controls_all <- c(controls_women, controls_hh)
controls_formula <- paste(controls_all, collapse = " + ")


for (i in outcomes_work) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula))
  model_i <- tryCatch({
    svyglm(formula_i, design = mysurvey_women
    ) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_12[[i]] <- model_i
  }
} 

tbl_list <- lapply(model_results_12, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_3
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


```




