---
title: "results"
author: "Ananya Mazumder"
date: "2026-01-28"
output: word_document
---
While there exists in the literature many studies looking at casual associations between cash transfers and women’s empowerment, causal literature is rather sparser. Without casual estimates however, understanding the effects of a cash transfer can be difficult, particularly in scenarios where households may be beneficiaries to many different kinds of schemes, and as selection into application for the schemes itself may be an indicator of empowerment. Thus, it becomes necessary to follow a quasi-experimental approach, and exploit the pilot nature of the program in order to isolate its effects. Although the program was slated to begin in 2011, due to delays in implementation, it is generally acknowledged that the program only really started in 2012 (von Haaren and Klonner, 2021). Hence, eligibility for the pilot program would begin in 2012, and would continue till 2017, when the program became nationwide (PMMVY, insert ref). 
The empirical design used in the aforementioned paper is adopted from Ghosh and Kochar (2018) who aimed to utilize the comparison across eligible and ineligible birth cohorts in treatment and district areas to examine effects on mother and child health. They also bring up the very important drawback in the design which is program compliance: neither von Haaren and Klonner nor Agarwal and Katewa address this in their subsequent papers, assuming that either cohort eligibility or program eligibility predict compliance. There may be several ways to include program compliance also into the design, as I have chosen to do, which is to also look at women above the age of 21, as these women would had to have been either 19 years of age or above to participate. This does not fully remediate the question of whether there was some fuzzy compliance i.e. whether age was strictly adhered to when it came to doling out program benefits. 
In order to parse out the effects of the cash transfer, I am conducting a differences-in-differences analysis, along the lines of Agarwal and Katewa (2024). The first difference would be between eligible women and ineligible women in the districts below, and the second would be between treated and control districts (as identified by von Haaren and Klonner, 2021). I am extending their approach by looking also at men’s attitudes towards decision-making and IPV, and also by utilizing a new dataset, namely the DHS 2019-21 data. The authors did not use this dataset as they were considering a policy disruption (i.e. the IGMSY becoming nationwide in 2017). Since I am looking at longer-term effects of the cash transfer on women who received the transfer between 2012-2016, the policy disruption should not (in cases where eligibility is in fact, restricted only to first birth) Additionally, effects would be an estimation of Intent-to-treat, as I do not have precise data on who opted for the scheme. Moreover, I am restricting eligibility to women who gave birth to either their first or second child between 2012-2016 i.e. program years, hence excluding women who might have benefited past 2019. 
Furthermore, I would also exclude the states of Odisha, Madhya Pradesh, Tamil Nadu and Maharashtra, as they have similar schemes at the state level. I am also excluding the Union Territories of Andaman and Nicobar, Ladakh, Daman & Diu, Lakshwadeep Islands, Chandigarh, Puducherry, Jammu and Kashmir. Nagaland is also excluded, as the district borders in the DHS were not compliant with the DHLS, which was used by von Haaren and Klonner (2020) to match districts originally.  The “low”, “medium” and “high” classifications refer to the grouping of these districts based upon their composite scores across various socioeconomic indicators. The scores were in turn used to find control districts in neighboring regions, and this setup works because the pilot program was not aimed at low-performing regions only—rather, aimed towards a group that would be representative of the country as a whole. 

Regression Equation: same as Agarwal & Katewa 

Yidst = αd + β1(treated_districtd*eligibility_statusit) + (λs*eligibility_status) + treated_district + χ(Xi)+γ(Xh)+ δihdst (1) 

Where: B1 is the coefficient of interest, or the one capturing the interaction effect between the treated district and the eligibility status, also λs*eligibility_status represents state-specific time trends. Eligibility status is a woman of Age 21 or above who gave birth to her first child between 2012-2016 or  a woman who gave birth to her second child during this same time period. Ineligibility is correspondingly, a woman of the same age who gave birth to either her first or second child between 2005-2009. This gives me a sample of four years both ways. 
Individual level controls include woman’s/man's age, square of woman’s/man's age, woman’s/man's education, woman’s/man's height and weights, age of woman at the first marriage, relative education of woman with respect to husband, husband’s education, and frequency of alcohol consumption by husband/partner. Household level controls include age of household head, sex of the household head, number of members in the household, number of children below 5 years in the household, household’s wealth index within a state, urban/rural residence, whether the household belongs to the SC (which in the DHS is coded as ethnicity), whether the household is poor in terms of the wealth index in the NHFS sample, household’s relative wealth based on the assets owned. 

Empowerment in this thesis would be looked at through various lenses, including decision-making, economic, sexual and reproductive rights and physical mobility. Accordingly, the outcomes looked at include woman's participation in decision making regarding various decisions in the household and with regard to her own mobility, women's economic means, healthcare practises and reproductive rights, in addition to her own attitudes towards violence. As established earlier in the introduction and literature review, an important key component of women's empowerment is the attitude of men. Subsequently, outcomes with regards to this include men's attitudes towards decision-making, violence and women's health.

```{r "setting up the data", include=FALSE, echo=FALSE}
library(haven)
library(tidyverse)
library(survey)
library(gtsummary)
library(xfun)
library(broom)
library(here)
library(labelled)
library(tableone)

data_2019 <- read_stata(here("data", "2019_final.dta"))

data_2019 <- data_2019 %>%
  mutate(
    v131 = to_factor(v131),
    v131 = case_when(
      v131 %in% c("caste", "tribe", "no caste / tribe", "don't know") ~ v131,
      TRUE ~ factor(NA, levels = levels(v131))    
      ) %>%
      set_variable_labels(v131 = "ethnicity")
  )

data_2019 <- data_2019 %>%
  mutate(
    v437 = case_when(
      v437 < 9000 ~ v437 / 10,
      TRUE ~ NA_real_
    ),
    v438 = case_when(
      v438 < 9000 ~ v438 / 10,
      TRUE ~ NA_real_
    )
  ) %>%
  set_variable_labels(
    v437 = "Weight (kg)",
    v438 = "Height (cm)"
  )

var_labels <- data_2019 %>% 
  map(~attr(., "label")) %>% 
  compact()

data_2019 <- data_2019 %>%
  mutate(across(everything(), ~{
    if (is.labelled(.)) {
      lbls <- val_labels(.)
      return(if_else(. >= 95 & . %in% lbls, NA_real_, as.numeric(.)))
    }
    return(.)
  })) %>%
  unlabelled() %>%
  mutate(across(where(is.numeric), ~zap_labels(.)))

data_2019 <- data_2019 %>% 
  mutate(treated_district = ifelse(
    shdist %in% c(214, 367, 273, 220, 169, 930, 871, 122, 130, 291, 
                  825, 302, 287, 328, 339, 248, 60, 357, 242, 842, 
                  412, 69, 470, 36, 321, 847, 488, 900, 562, 49, 
                  581, 546, 28, 593, 585), 1, 0
  ))

data_2019 <- data_2019 %>% 
  mutate(eligibility_status = case_when(
    v012 >= 21  & 
      ((b2_01 >= 2012 & b2_01 <= 2016) | 
         (b2_02 >= 2012 & b2_02 <= 2016 & !is.na(b2_02))) ~ 1,
    
    v012 >= 21  &
      ((b2_01 >= 2005 & b2_01 < 2009) | 
         (b2_02 >= 2005 & b2_02 < 2009 & !is.na(b2_02))) ~ 0,
  ))


data_2019 <- data_2019 %>% 
  set_variable_labels(.labels = var_labels, .strict = FALSE)

data_2019$wt_women <- data_2019$v005/1000000
data_2019$wt_men <- data_2019$mv005/1000000
data_2019 <- data_2019 %>%
  mutate(
    combined_group = interaction(
      haven::as_factor(eligibility_status), 
      haven::as_factor(treated_district), 
      sep = " × "
    )
  )
data_2019$v012_sq <- data_2019$v012^2
attr(data_2019$v012_sq, "label") <- "Square of Women's Age"

controls_hh <- c("v131","v136","v137","v151","v152","v119","v120", "v121", "v122", "v123", "v124", "v125", "mv190", "sm190s")
controls_women <- c("v012", "v012_sq", "v133","v437", "v438", "v511", "d113", "v201", "v715", "v714")
controls_men <- c("mv035", "mv133", "mv212", "mv190a", "sm190s") ##added also the wealth indices

group_counts <- data_2019 %>%
  filter(!is.na(combined_group)) %>%
  count(combined_group) %>%
  arrange(combined_group)

data_men <- data_2019 %>% filter(!is.na(mv021))

mysurvey_men <- svydesign(
  id = ~mv021, 
  strata = ~mv022,
  weights = ~wt_men,
  data = data_men,
  nest = TRUE
)

mysurvey_women <- svydesign(
  id = ~v021,
  strata = ~v022, 
  weights = ~wt_women,
  data = data_2019,
  nest = TRUE
)

options(survey.lonely.psu = "adjust") 

outcomes_dec <- c("v739", "v743a", "v743b", "v743d", "v743f") 
outcomes_ipv <- c("d106", "d107", "d108", "d129")
outcomes_work <- c("v714", "v714a", "v746", "v731")

```

The following is a Balance Table for the women who are characterised as "ineligible" as their first/second children are born prior to 2011. 
```{r "Balance Table", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
data_balance <- data_2019 %>%
  filter(
    b2_01 < 2011, 
    b2_02 < 2011
  )

balance_survey <- svydesign(
  id = ~v021,
  strata = ~v022, 
  weights = ~wt_women,
  data = data_2019,
  nest = TRUE
) 
options(survey.lonely.psu = "adjust")

balance_table <- balance_survey %>%
  tbl_svysummary(
    include = c(all_of(outcomes_dec), 
                all_of(controls_hh), 
                all_of(controls_women)),
    by = treated_district,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  ) %>%
  add_overall() %>%
  add_p(
    test = list(all_continuous() ~ "svy.t.test",
                all_categorical() ~ "svy.wald.test"),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
  modify_header(label = "**Characteristic**") %>%
  modify_caption("**Table 1. Balance Test: Comparison of Means (Pre-2011 Births Only)**") %>%
  modify_table_body(
    ~.x %>% 
      filter(row_type == "label")
  )

balance_table %>% as_gt()
```
 What follows are descriptive tables for the household and individual level controls. 

```{r "First descriptive table", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}

desc_table_1 <- mysurvey_women %>%
  tbl_svysummary(
    include = all_of(c(controls_women, controls_hh)),
    by = combined_group,
    statistic = list(
      all_continuous() ~ "{mean}\n({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 3,
    missing = "no"
  ) %>%
  modify_caption("**Table 2. Survey-Weighted Descriptives for Women & Household**") %>%
  modify_header(
    stat_1 ~ paste0("**Control District × Ineligible**  \nN = ", group_counts$n[1]),
    stat_2 ~ paste0("**Treated District × Ineligible**  \nN = ", group_counts$n[2]), 
    stat_3 ~ paste0("**Control District × Eligible**  \nN = ", group_counts$n[3]),
    stat_4 ~ paste0("**Treated District × Eligible**  \nN = ", group_counts$n[4])
  ) %>%
  modify_footnote(all_stat_cols() ~ "Mean (SD) for continuous variables; N (%) for categorical variables. N represents unweighted sample size.Wealth indices: 1 = Poorest, 5 = Richest. Sex of HH head: 1 = Male, 2 = Female. Binary variables: 0 = No, 1 = Yes, 7 = Not a dejure resident (where applicable). For all indicators based on the household members (PR file), either the de jure population (usual resident of the house) or the de facto population (slept at the home last night) is selected.")

desc_table_1 %>% as_gt()
```

the next is a descriptive table for men, and their characteristics. 

```{r "Second descriptive-table", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
desc_table_2 <- mysurvey_men %>%
  tbl_svysummary(
    include = all_of(controls_men),
    by = combined_group,
    statistic =list(
      all_continuous() ~ "{mean}\n({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 3,
    missing = "no"
  ) %>%
  add_n() %>% 
  modify_caption("**Table 3. Survey-Weighted Descriptives for Men**") %>%
  modify_header(
    stat_1 ~ paste0("**Control District × Ineligible**  \nN = ", group_counts$n[1]),
    stat_2 ~ paste0("**Treated District × Ineligible**  \nN = ", group_counts$n[2]), 
    stat_3 ~ paste0("**Control District × Eligible**  \nN = ", group_counts$n[3]),
    stat_4 ~ paste0("**Treated District × Eligible**  \nN = ", group_counts$n[4])
  ) %>%
  modify_footnote(all_stat_cols() ~ "Mean (SD) for continuous variables; N (%) for categorical variables. 0 = no, 1 = yes for binary variables.")
desc_table_2 %>% as_gt() 
```

The table above displays certain characteristics of men in the sample. These men are married, and matched to women in the sample. 


Regressions

````{r "women's decision-making models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_dec <- c("v739", "v743a", "v743b", "v743d", "v743f") 

model_results_1 <- list()
for (i in outcomes_dec) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status * treated_district"))
  model_i <- tryCatch({
    svyglm(formula_i, design = mysurvey_women)  
  }, 
  error = function(e) {
    message(paste("Error fitting model for", i, ":", e$message)) 
    return(NULL)
  }) 
  
  if (!is.null(model_i)) {
    model_results_1[[i]] <- model_i
  }
}

custom_labels <- c(
  "Own Earnings",
  "Own Healthcare", 
  "Large Purchases",
  "Visiting Family",      
  "Husband's Money"  
)

tbl_list <- lapply(model_results_1, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_labels
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

model_results_2 <- list()
for (i in outcomes_dec) {
  
  controls_all <- c(controls_women, controls_hh)
  controls_formula <- paste(controls_women, collapse = " + ")
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula))   
  model_i <- tryCatch({
    svyglm(formula_i, design = mysurvey_women)  
  }, 
  error = function(e) {
    message(paste("Error fitting model for", i, ":", e$message)) 
    return(NULL)
  }) 
  
  if (!is.null(model_i)) {
    model_results_2[[i]] <- model_i
  }
}

tbl_list <- lapply(model_results_2, function(model) {  
  tbl_regression(
    model,
    include = c("eligibility_status", "treated_district", "eligibility_status:treated_district"),
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_labels
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


````

These are my main results, the effect of eligibility interacted with treated district on decision-making at various household dimensions. 

```{r, "IPV Models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_ipv <- c("d106", "d107", "d108", "d129")
model_results_3 <- list()
for (i in outcomes_ipv) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  model_i <- tryCatch({
    svyglm(formula_i, design= mysurvey_women)
  }, 
  error= function(e){
    message(paste("Error fitting model for", i, ":", e$message)) 
    return(NULL)
  })
  
  if (!is.null(model_i)) {
    model_results_3[[i]] <- model_i
  }
}
custom_2 <- c("Less Severe Violence", "Severe Violence", "Sexual Violence", "Afraid of Husband")

tbl_list <- lapply(model_results_3, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_2
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


##Regressions with controls ##
outcomes_ipv <- c("d106", "d107", "d108", "d129")
model_results_4 <- list()
for (i in outcomes_ipv) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula)) 
  model_i <- tryCatch({
    svyglm(formula_i, design= mysurvey_women)
    }, 
  error= function(e){
    message(paste("Something got messed up somehow", i, ":", e$message)) 
    return(NULL)
  })
  
  if (!is.null(model_i)) {
    model_results_4[[i]] <- model_i
  }
}

tbl_list <- lapply(model_results_4, function(model) {  
  tbl_regression(
    model,
    include = c("eligibility_status", "treated_district", "eligibility_status:treated_district"),
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_2
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()
```
Of particular interest in my thesis is the attitude of men towards decision-making and IPV as well. 

Men's Attitudes towards violence, and IPV, decision-making
```{r, "Men's Models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_men_1 <-c("mv633a", "mv633b", "mv633d", "mv634a", "mv634b", "mv634c", "mv634d") ##wife can refuse sex
outcomes_men_2 <-c("mv739", "mv743a", "mv743b") #person who decides on certain things
outcomes_men_3 <-c("mv744a", "mv744b", "mv744c", "mv744d", "mv744e") #violence justified 
custom_men_1 <-c("Refuse in case husband has sti", "Refuse in case husband has other women", "Refuse in case wife is tired", 
                 "Refuse: right to get angry", "Refuse: right to withhold financial means", "Refuse: right to use force", 
                 "Refuse, right to have sex with another woman")
custom_men_1 <-c("Refuse sex in case husband has sti", "Refuse sex in case husband has other women", "Refuse sex in case wife is tired", 
                 "Refuse sex: right to get angry", "Refuse sex: right to withhold financial means", "Refuse sex: right to use force", 
                 "Refuse sex, right to have sex with another woman")
custom_men_2 <-c("Own Earnings", "Healthcare", "Large Purchases")
custom_men_3 <-c("Justified: wife goes out without telling", "Justified: wife neglects the children", "Justified: wife argues with husband", "Justified: wife refuses to have sex", "Justified: wife burns food")

##Refusing sex Models without controls##
model_results_5 <- list()

for (i in outcomes_men_1) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_5[[i]] <- model_i
  }
} 
tbl_list <- lapply(model_results_5, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_1
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


##Decision making models without controls ##
model_results_6 <- list()

for (i in outcomes_men_2) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_6[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_6, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_2
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

## Violence models, without controls
model_results_7 <- list()

for (i in outcomes_men_3) {
  
  controls_formula <- paste(controls_women, collapse = " + ")
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status")) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_7[[i]] <- model_i
  }
} 


## summarizing output 
tbl_list <- lapply(model_results_7, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_3
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()


##Men Models with controls##

model_results_8 <- list()

for (i in outcomes_men_1) {
  controls_all_men <- c(controls_men, controls_hh)
  controls_formula <- paste0(controls_all_men, collapse = " + ")
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula))
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men)
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_8[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_8, function(model) {  
  tbl_regression(
    model,
    include = c("eligibility_status", "treated_district", "eligibility_status:treated_district"),
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_1
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

##Decision making models with controls ##
model_results_9 <- list()

for (i in outcomes_men_2) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula)) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_9[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_9, function(model) {  
  tbl_regression(
    model,
    include = c("eligibility_status", "treated_district", "eligibility_status:treated_district"),
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_2
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

## Violence models, without controls
model_results_10 <- list()

for (i in outcomes_men_3) {
  
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula)) 
  
  model_i <- tryCatch({
    
    svyglm(formula_i, design = mysurvey_men) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_10[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_10, function(model) {  
  tbl_regression(
    model,
    include = c("eligibility_status", "treated_district", "eligibility_status:treated_district"),
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_men_3
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

```

Lastly, the effect of eligibilityxtreated district for the Economic Participation of Women is looked at. 

```{r, "Women's Economic Participation Models", warning=FALSE, message=FALSE, include=TRUE, echo=FALSE}
outcomes_work <- c("v714", "v714a", "v746", "v731")
model_results_11 <- list()
custom_3 <- c("currently working", "has a job, currently absent", "earns more than husband", "worked in last 12 months")

for (i in outcomes_work) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status"))
  model_i <- tryCatch({
    
    svyglm(formula_i, 
           design = mysurvey_women,
    ) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_11[[i]] <- model_i
  }
} 


tbl_list <- lapply(model_results_11, function(model) {  
  tbl_regression(
    model,
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_3
) %>%
  modify_caption("Survey-Weighted DiD Results, No Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

##with controls 
model_results_12 <- list()
controls_all <- c(controls_women, controls_hh)
controls_formula <- paste(controls_all, collapse = " + ")


for (i in outcomes_work) {
  formula_i <- as.formula(paste0(i, " ~ eligibility_status + treated_district * eligibility_status + ", controls_formula))
  model_i <- tryCatch({
    svyglm(formula_i, design = mysurvey_women
    ) 
    
  }, 
  error = function(e){
    message(paste("no; something is wrong somehow", i, ":", e$message)) 
    return(NULL)
  } 
  ) 
  
  if (!is.null(model_i)) {
    model_results_12[[i]] <- model_i
  }
} 

tbl_list <- lapply(model_results_12, function(model) {  
  tbl_regression(
    model,
        include = c("eligibility_status", "treated_district", "eligibility_status:treated_district"),
    label = list(
      eligibility_status ~ "Eligibility Status",
      treated_district ~ "Treated District",
      `eligibility_status:treated_district` ~ "Eligibility × Treated"
    ),
    estimate_fun = function(x) style_number(x, digits = 3),
    pvalue_fun = function(x) style_pvalue(x, digits = 3)
  ) %>%
    modify_column_merge(pattern = "{estimate} ({std.error})") %>%
    modify_column_hide(c(conf.low, conf.high)) %>%
    add_glance_table(include = nobs)  
})

# Combine all models into one table
tbl_merge(
  tbls = tbl_list,
  tab_spanner = custom_3
) %>%
  modify_caption("Survey-Weighted DiD Results, Controls") %>%
  modify_footnote(
    everything() ~ "Coefficients with standard errors in parentheses."
  ) %>%
  as_flex_table()

```




